---
title: "Activity: Nuclear Reactors"
author: "Madeline Mucciolo"
output: html_notebook
---

```{r}
library(tidyverse)
```
- Load *tidyverse* into the environment for later use.

## Scrape the Data 

```{r}
library(rvest)

page <- "https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors"
tableList <- page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)
```
- Scraping the data from the Wiki Page and storing it in **tableList**.  

```{r}
Japan <- tableList[[21]]
head(Japan)
```
- After searching through **tableList**, I found Japan to be the 21st element in the list. I took that data, and stored it in a new variable named **Japan**.  

## Your turn: In what ways is the table tidy? How is it not tidy? What’s different about it from a tidy table?
- The table is tidy because each column is a variable with the same type of value for each row. Most of the rows represent the nuclear reactors [each case is the Name of the plant and the UnitNo. of that specific reactor].

- However, the table is not tidy because the first row does is a repeat of the column names, which means it does not represent the same underlying case as all of the other rows. Some variable names are long and have spaces.


## Your Turn: Plot Net Generation Capacity vs Construction Date

```{r}
#my code here 


```


## Your Turn: Scrape & Clean China Data (then merge with Japan)

```{r}
#my code here... 

```



## Your Turn: Reconstruct Info Graphic of Japan Reactors (or other country of interest)

```{r}
#My code here

```